Distanced-based VOCC analysis

### 2019-05-17 analysis/VOCC/dist-vocc.Rmd
refining plot, calcslope, and analysis function

# add and scale predictors after filtering for survey(s) of interest
data <- all_depth$data %>%
  filter(depth_m>10) %>% # removes data if sensor stayed too near surface
  # filter(ssid != 1) %>%
  # filter(ssid != 3) %>%
  # filter(ssid != 4) %>%
  # filter(ssid != 16) %>%
  gfplot:::scale_survey_predictors()

@@

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
# # choose the spatial range to model
dat <- data %>% dplyr::filter(year > 2003) %>% select(year, ssid, X, Y, temperature_c, depth_scaled, depth_scaled2)
nd <- nd #%>% filter(ssid == 4)

@@

Calculate predicted values
```{r}
m_temp <- readRDS("../VOCC/data/m_temp_post2003.rds")
# m_temp <- readRDS("../VOCC/data/m_temp_allyears.rds")

@@

p <- plot_map(predictions , "est") +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
print(p)
```
```{r}
# choose the spatial range to build raster on
predicted1 <- predictions %>% filter(ssid == 1) 
predicted3 <- predictions %>% filter(ssid == 3) 
predicted4 <- predictions %>% filter(ssid == 4) 
predicted16 <- predictions %>% filter(ssid == 16) 
predicted1n3 <- predictions %>% filter(ssid != 16) %>% filter(ssid != 4) %>% filter(year > 2004)

@@

make_vector_data <- function(climate_data, 
  ssid = NULL,
  start_year = NULL,
  input_cell_size = 2, 
  scale_fac = 2,
  delta_t_total = 10,
  delta_t_step = 2,
  time_slices = 7, 
  indices = c(1, 1, 2, 2, 2, 3, 3),
  thresholds = c(0.75)
  ) {
#browser()
if (!is.null(ssid)) climate_data <- climate_data[climate_data$ssid %in% ssid, ]
if (!is.null(start_year)) climate_data <- climate_data %>% dplyr::filter(year >= start_year)

@@

start_data #
end_data  #

out <- dist_based_vocc(
  start_data = start_data,
  end_data = end_data,
  x = "x",
  y = "y",
  variable_names = c("index_1"), # what the layer within each element is called
  thresholds = thresholds,
  cell_size =  input_cell_size*scal_fac,
  delta_t = delta_t_total,
  raster = TRUE
  )

# FIXME: need to change function to deal with different time steps within a brick
slopedat <-  calcslope(rbrick, delta_t = delta_t_step) # vocc::calcslope for comparison
out <- left_join(out, slopedat, by = c("x", "y")) %>% select(-icell)
out$C_per_decade <- out$slope * 10
out$km_per_decade <- (out$distance/delta_t)*10 
out
}

make_vector_data (predictions, 
  ssid = c(1, 3),
  start_year = 2005,
  input_cell_size = 2, 
  scale_fac = 2,
  delta_t_total = 10,
  delta_t_step = 2,
  time_slices = 7,
  indices = c(1, 1, 2, 2, 2, 3, 3),
  thresholds = c(0.75)
  )
```

>>>>

# add and scale predictors after filtering for survey(s) of interest
data <- all_depth$data %>%
  filter(depth_max>10) %>% # removes data if sensor stayed too near surface
  # filter(ssid != 1) %>%
  # filter(ssid != 3) %>%
  # filter(ssid != 4) %>%
  # filter(ssid != 16) %>%
  gfplot:::scale_survey_predictors()

@@

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
# # choose the spatial range to model
dat <- data %>% dplyr::filter(year > 2003) #%>% select(year, ssid, X, Y, temperature_c, depth_scaled, depth_scaled2)
nd <- nd #%>% filter(ssid == 4)

@@

Calculate predicted values
```{r}
# m_temp <- readRDS("../VOCC/data/m_temp_post2003.rds")
 m_temp <- readRDS("../VOCC/data/m_temp_allyears.rds")

@@

p <- plot_map(predictions , "est") +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
print(p)
```

```{r}
# choose the spatial range to build raster on
predicted1 <- predictions %>% filter(ssid == 1) 
predicted3 <- predictions %>% filter(ssid == 3) 
predicted4 <- predictions %>% filter(ssid == 4) 
predicted16 <- predictions %>% filter(ssid == 16) 
predicted1n3 <- predictions %>% filter(ssid != 16) %>% filter(ssid != 4) %>% filter(year > 2004)

@@

```{r}
make_vector_data <- function(climate_data, 
  ssid = NULL,
  start_year = NULL,
  input_cell_size = 2, 
  scale_fac = 2,
  delta_t_total = 10,
  delta_t_step = 2,
  time_slices = 7, 
  indices = c(1, 1, 2, 2, 2, 3, 3),
  thresholds = c(0.75)
  ) {

if (!is.null(ssid)) climate_data <- climate_data[climate_data$ssid %in% ssid, ]
if (!is.null(start_year)) climate_data <- climate_data %>% dplyr::filter(year >= start_year)

@@

out <- dist_based_vocc(
  start_data = start_data,
  end_data = end_data,
  x = "x",
  y = "y",
  variable_names = c("index_1"), # what the layer within each element is called
  thresholds = thresholds,
  cell_size =  input_cell_size*scale_fac,
  delta_t = delta_t_total,
  raster = TRUE
  )

# FIXME: need to change function to deal with different time steps within a brick
slopedat <-  calcslope(rbrick, delta_t_step = delta_t_step) # vocc::calcslope for comparison
out <- left_join(out, slopedat, by = c("x", "y")) %>% select(-icell)
out$C_per_decade <- out$slope * 10
out$km_per_decade <- (out$distance/delta_t_total)*10 
out
}

```{r}
out <- make_vector_data (predictions, 
  ssid = c(1, 3),
  start_year = 2005,
  input_cell_size = 2, 
  scale_fac = 2,
  delta_t_total = 10,
  delta_t_step = 2,
  time_slices = 7,
  indices = c(1, 1, 2, 2, 2, 3, 3),
  thresholds = c(0.75)
  )
glimpse(out)
```

```{r}
gvocc <- plot_vocc(out,
  low_col = "white",
  mid_col = "white",
  high_col = "grey97", 
  vec_aes = "distance",
  vec_lwd_range = c(0.5,0.6),
  max_vec_plotted = 100,
  fill_col = "var_1_s",
  fill_label = "Mean\ntemperature\n2005 & 2007",
  raster_alpha = 1,
  vec_alpha = 0.8
)
gvocc
```

```{r}
gtrend <- plot_vocc(out,
  fill_col = "C_per_decade",
  fill_label = "Temperature\ntrend (°C/decade)\nfor 2005-2017",
  raster_alpha = 1,
  vec_aes = NULL
)
gtrend
```

```{r}
# png(file = "accasp-wg-fig.png",   # The directory you want to save the file in
# res = 600,
# units = 'in',
# width = 10, # The width of the plot in inches
# height = 7) # The height of the plot in inches

gridExtra::grid.arrange(gtrend, gvocc, nrow = 1)
#dev.off()
```
